### 2023-09-26 doc/_multienv_results.qmd
small changes to figure caption

![**Multi-environment fitness inference.** (A) Schematic of the simulated
experimental design where growth-dilution cycles were performed in different
environments in a cycle. (B) log frequency rations between adjacent time points.
Darker lines represent the neutral barcodes. The colors in the background demark
the corresponding environment, matching colors in (A). (C-E) Comparison between
the ground truth fitness value from the logistic-growth simulation and the
inferred fitness value for each environment. Gray error bars represent the 68\%
posterior credible region. (F) The empirical cumulative distribution function
(ECDF) for the absolute z-score value of the ground truth parameter value within
the inferred fitness posterior distribution for all fitness values (black line)
and each environment individually (color lines). (G) Examples of the posterior
predictive checks for all neutral lineages (upper left panel) and a subset of
representative mutant lineages. Shaded regions represent the 95\%, 68\%, and 5\%
credible regions for the data. The reported errors above the plot represent the
68\% credible region on the mutant relative fitness marginal distribution.
Background colors match those of (A).](./figs/fig06){#fig-06}

>>>>

![**Multi-environment fitness inference.** (A) Schematic of the simulated
experimental design where growth-dilution cycles are performed into different
environments for each cycle. (B) log frequency rations between adjacent time
points. Darker lines represent the neutral barcodes. The colors in the
background demark the corresponding environment, matching colors in (A).
Environment 2 is set to have, on average, half the growth rate of environment 1.
Likewise, environment 3 is set to have, on average, twice the growth rate of
environment 1. (C-E) Comparison between the ground truth fitness value from the
logistic-growth simulation and the inferred fitness value for each environment.
Gray error bars represent the 68\% posterior credible region. (F) The empirical
cumulative distribution function (ECDF) for the absolute z-score value of the
ground truth parameter value within the inferred fitness posterior distribution
for all fitness values (black line) and each environment individually (color
lines). (G) Examples of the posterior predictive checks for all neutral lineages
(upper left panel) and a subset of representative mutant lineages. Shaded
regions surrounding the data represent the 95\%, 68\%, and 5\% credible regions
for the data. The reported errors above the plot represent the 68\% credible
region on the mutant relative fitness marginal distribution. Background colors
match those of (A).](./figs/fig06){#fig-06}
